Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/design.tex

We present both a systematic overview of Nail's syntax with short examples in
Figure~\ref{fig:syntax} shows the elements of Nail grammars and explain our design in more detail
below, using a grammar for the well-known DNS protocol as a guiding example.

>>>>

We present both a systematic overview of Nail's syntax with short examples
in Figure~\ref{fig:syntax}, and explain our design in more detail below,
using a grammar for the well-known DNS protocol as a running example
(shown in Figure~\ref{fig:dns-full}).
